Free Theorems for Nested Types

### 2020-07-02 submitted-POPL-2021/paper-final.tex
updated submission

It is well-known that there are no set-based parametric models of
System F~\cite{rey84}. So it is worth noting that our calculus does
not contain all System F types, and in fact is not impredicative, so a
set-based parametric model is not {\em a priori} precluded. In fact,
the local finite presentability of $\set$ makes it an obvious choice
for interpreting nested types. We return to this point in
Section~\ref{sec:conclusion}.

@@

We are not the first to consider parametricity at higher
kinds. Atkey~\cite{atk12} constructs a parametric model for full
System $F_\omega$, but within the impredicative Calculus of Inductive
Constructions (iCIC) rather than in a semantic category. His
construction is in some ways similar to ours, but it represents data
types using Church encodings rather than constructing them via
primitives. However, the $\mathit{fmap}$ functions associated to 
Atkey's functors must be {\em given} together with their
underlying type constructors, and he need not 
impose cocontinuity conditions on his model to ensure that 
fixpoints of his functors exist. Unfortunately, Atkey does not 
indicate which
type constructors support the $\mathit{fmap}$ functions
needed for them to be functors, but we suspect spelling this
out explicitly would result in a full higher-kinded extension of the
calculus presented here.
\section{The Calculus}\label{sec:calculus}

>>>>

It is well-known that there are no set-based parametric models of
System F~\cite{rey84}. So it is worth noting that our calculus does
not contain all System F types, and is not impredicative, so a
set-based parametric model is not {\em a priori} precluded. In fact,
local finite presentability of $\set$ makes it an obvious choice for
interpreting nested types. We return to this point at several places
below.

@@

We are not the first to consider parametricity at higher
kinds. Atkey~\cite{atk12} constructs a parametric model for full
System $F_\omega$, but within the impredicative Calculus of Inductive
Constructions rather than in a semantic category. His
construction is in some ways similar to ours, but it represents data
types using Church encodings rather than constructing them via
primitives. However, the $\mathit{fmap}$ functions associated to 
Atkey's functors must be {\em given} together with their
underlying type constructors, and he need not 
impose cocontinuity conditions on his model to ensure that 
fixpoints of his functors exist. Unfortunately, Atkey does not 
indicate which
type constructors support the $\mathit{fmap}$ functions
needed for them to be functors, but we suspect spelling this
out explicitly would result in a full higher-kinded extension of the
calculus presented here.
\section{The Calculus}\label{sec:calculus}
